Blaming the Typeless: \\ Scalable, Human-Centric Python Localization

### 2018-08-25 paper/main.tex
minor changes

To apply machine learning to analyze the data, we have to formulate the
problem into standard classification problem.
The corresponding label, is represented as $1$ and $0$, which means whether
the term of a program pair (a buggy and a fixed program) is blamed or not.
This is a binary classification problem.
For each term of a program pair, we extracted the features mentioned in
Section \ref{sec-features}.
By performing one-hot encoding on categorical features, we can represent the
extracted features into a length $M$ feature vector $\mathbf{x} \in
\mathcal{R}^{M}$.

The notations are defined as follows.
Let the number of examples be $N$.
Given a dataset $\mathcal{D} \in \{\mathbf{x}^{(i)}, y^{(i)}\}^{N}_{i=1}$,
where $\mathbf{x}^{(i)} \in \mathcal{R}^{M}$ and $y^{(i)} \in \{0, 1\}$,
a learning model will learn a function $f: \mathbf{R}^{M} \to \{0, 1\}$.
Due to the large amount of data provided in this task, we only consider the
following models which are scalable to large dataset.

\emph{Decision Tree}
Decision tree~(DT) learns a tree of binary predicates over the features and
recursively partitioning the feature space until specific criteria is met.
The usual stopping criteria is the number of data in a node falls below a
certain threshold.
%
Each node in the tree contains a single thresholding binary classifier
$[ \mathbf{x}_i \leq t ]$, $[ \cdot ]$ is the indicator function.
$i$ is greedly selected to minimize the impurity of the training data.
The impurity is usually measured by gini index
\cite{breiman2017classification} or entropy \cite{quinlan1986induction}.
This thresholding classifier determines that during prediction, whether a
given input should proceed down the left or right subtree.
%
Each leaf is labeled with a prediction and the fraction of
correctly-labeled training samples that would reach it; the latter
quantity can be interpreted as the decision tree's confidence in its
prediction.
%
This leads to a non-linear prediction rule which can be more expressive
then linear model like LR depending on the data used to build it.
%Training a decision tree entails finding both a set of good partitioning
%predicates and a good ordering of the predicates based on data.
%
There are several implementations of DT such as C4.5
\cite{quinlan2014c4} and CART \cite{breiman2017classification}.

>>>>

To apply machine learning for analysis of the data, we have to formulate the
problem into standard classification problem.
The corresponding label, is represented as $1$ and $0$, which means whether
the term of a program pair (a buggy and a fixed program) is blamed or not.
This is a binary classification problem.
For each term of a program pair, we extracted the features mentioned in
Section \ref{sec-features}.
By performing one-hot encoding on categorical features, we can represent the
extracted features into a length $M$ feature vector $\mathbf{x} \in
\mathcal{R}^{M}$.

The binary classification problem is defined as follows.
Let the number of examples be $N$.
Given a dataset $\mathcal{D} \in \{\mathbf{x}^{(i)}, y^{(i)}\}^{N}_{i=1}$,
where $\mathbf{x}^{(i)} \in \mathcal{R}^{M}$ and $y^{(i)} \in \{0, 1\}$,
a learning model will learn a function $f: \mathbf{R}^{M} \to \{0, 1\}$.
Due to the large amount of data provided in this task, we only consider the
following models which are scalable to large dataset.

\emph{Decision Tree}
Decision tree~(DT) learns a tree of binary predicates over the features and
recursively partitioning the feature space until specific criteria is met.
The usual stopping criteria is the number of data in a node falls below a
certain threshold.
%
Each node in the tree contains a single thresholding binary classifier
$[ \mathbf{x}_i \leq t ]$, $[ \cdot ]$ is the indicator function.
$i$ is greedly selected to minimize the impurity of the training data.
The impurity is usually measured by gini index
\cite{breiman2017classification} or entropy \cite{quinlan1986induction}.
This thresholding classifier determines that during prediction, whether a
given input should proceed down the left or right subtree.
%
Each leaf is labeled with a prediction and the fraction of
correctly-labeled training samples that would reach it; the latter
quantity can be interpreted as the decision tree's confidence in its
prediction.
%
This leads to a non-linear prediction rule which can be more expressive
then linear model like LR depending on the data used to build it.
%Training a decision tree entails finding both a set of good partitioning
%predicates and a good ordering of the predicates based on data.
%
There are several implementations of DT such as C4.5 \cite{quinlan2014c4},
ID3 \cite{quinlan1986induction} and CART \cite{breiman2017classification}.
